\LARGE \bf Experimental Validation of Reference Spreading by Robotic Manipulation of Unmodeled Objects

### 2023-01-03 QP.tex
43we

\text{\textbf{Reference Spreading}}\\
\varphi  \quad \text{Time of impact}\\
\gamma  \quad \text{Normalized time since impact}\\
T  \quad \text{Duration of interim impact mode}\\
m \quad \text{Intermediate impact mode selector (0: no RS, 1: Jari, 2: Sven, 3: mixing)}\\\\
\text{\textbf{Sub- and superscripts}}\\
(\cdot)^{a} \quad \text{Ante-impact signal}\\
(\cdot)^{p} \quad \text{Post-impact signal}\\
(\cdot)_{dem} \quad \text{Signals from VR device during recording}\\
(\cdot)_{rec} \;\quad \text{Signals measured from robot or calculated during recording}\\
(\cdot)_{ref} \;\quad \text{Signals determined using RS scheme}\\
(\cdot)_{rep} \;\quad \text{Signals measured from robot or calculated during replay}\\
\end{array}$
\newpage
\section*{Recording}

@@

\section*{Replaying}
$\begin{array}{l}
\ddot{q}_{rep} = \min\limits_{\ddot{q}}\left \|  \begin{bmatrix}
\alpha(\ddot{q})\\ 
a(\ddot{q})
\end{bmatrix} - \Lambda^{-1}(f_{rep}+f_{rec}) \right \| + \left \|\ddot{q}_1-(\beta_{rep}+\beta_{rec}) \right \|\\\\
f_{rep} =2(\Lambda K_{rep})^{\frac{1}{2}} \begin{bmatrix}
\omega_{rec} - \omega_{rep}
\\ 
v_{rec}-v_{rep}
\end{bmatrix} + K_{rep} \begin{bmatrix}
R_{rep}(\log({R_{rep}}^TR_{rec}))^{\vee }\\ 
p_{rec}-p_{rep}
\end{bmatrix}\\\\
\beta_{rep} = 2\sqrt{k_{rep}}\left [ \dot{q}_{1,rec}-\dot{q}_{1,rep}  \right ] + k_{rep}\left [ q_{1,rec}-q_{1,rep}  \right ]
\end{array}$

\includegraphics[trim={1cm 17.8cm 5cm 6.5cm}, clip]{Graphics/qp.pdf}
\\
\section*{Reference Extending}
$\begin{array}{l}
REhold(x,t,\varphi) 
% = \begin{bmatrix} x^a(t) & x^p(t) \end{bmatrix} 
= \begin{cases} 
\begin{bmatrix} x(t) & x(\varphi) \end{bmatrix},& \text{if } t\leq \varphi\\
\begin{bmatrix} x(\varphi) & x(t) \end{bmatrix},& \text{if } t> \varphi\\
\end{cases}\\\\\\

REintergrate(x,y,t,\varphi) 
% = \begin{bmatrix} y^a(t) & y^p(t) \end{bmatrix} 
= \begin{cases} 
\begin{bmatrix} x(t) & x(\varphi) \end{bmatrix}+\begin{bmatrix}0 & y(\varphi)(t-\varphi) \end{bmatrix},& \text{if } t\leq \varphi\\
\begin{bmatrix} x(\varphi) & x(t) \end{bmatrix}+\begin{bmatrix}y(\varphi)(t-\varphi) & 0  \end{bmatrix},& \text{if } t> \varphi\\
\end{cases}\\\\

REintergrateRot(R,\omega,t,\varphi) 
% = \begin{bmatrix} y^a(t) & y^p(t) \end{bmatrix} 
= \begin{cases} 
\begin{bmatrix} R(t) & R(\varphi)e^{\omega(\varphi)(t-\varphi)} \end{bmatrix},& \text{if } t\leq  \varphi\\
\begin{bmatrix} R(\varphi)e^{\omega(\varphi)(t-\varphi)} & R(t) \end{bmatrix},& \text{if } t> \varphi\\
\end{cases}\\
\\

\begin{bmatrix} R_{rec}^a(t) & R_{rec}^p(t) \end{bmatrix} 
= REintergrateRot(R_{rec},\omega_{rec},t,\varphi_{rec}) \\
\\

\begin{bmatrix} 
p_{rec}^a(t) & p_{rec}^p(t) \\
 q_{1,rec}^a(t) & q_{1,rec}^p(t)
\end{bmatrix} = REintergrate(
\begin{bmatrix} 
p_{rec}\\
 q_{1,rec}
\end{bmatrix} 
,\begin{bmatrix} 
v_{rec}\\
 \dot{q}_{1,rec}
\end{bmatrix} 
,t,\varphi_{rec})\\
\\

\begin{bmatrix} 
\omega_{rec}^a(t)&\omega_{rec}^p(t)\\
v_{rec}^a(t)&v_{rec}^p(t)\\
 \dot{q}_{1,rec}^a(t)&\dot{q}_{1,rec}^p(t)\\
 f_{rec}^a(t)&f_rec^p(t)\\
 \beta_{rec}^a(t)&\beta_{rec}^p(t)
\end{bmatrix} = REhold(
\begin{bmatrix} 
\omega_{rec}\\
v_{rec}\\
 \dot{q}_{1,rec}\\
 f_{ref}\\
 \beta_{rec}
\end{bmatrix} 
,t,\varphi_{rec})\\
\end{array}$

@@

$\begin{array}{l}
\gamma_{rep} = \frac{t-\varphi_{rep}}{T}\\

RS(x^a(t),x^p(t),t,\gamma) = \begin{cases} 
x^a,& \text{if } \gamma \leq 0\\
x^p,& \text{if } \gamma \geq 1\\

x^p,& \text{if } (0< \gamma < 1)\wedge(m=0)\\ 
x^a,& \text{if } (0< \gamma < 1)\wedge(m=1)\\ 
x^a,& \text{if } (0< \gamma < 1)\wedge(m=2)\\ 
(1-\gamma)x^a+ \gamma x^p,& \text{if } (0< \gamma < 1)\wedge(m=3)\\ \end{cases}\\\\

RSvel(x,x^a(t),x^p(t),t,\gamma) = \begin{cases} 
x^a,& \text{if } \gamma \leq 0\\
x^p,& \text{if } \gamma \geq 1\\

x^p,& \text{if } (0< \gamma < 1)\wedge(m=0)\\ 
x,& \text{if } (0< \gamma < 1)\wedge(m=1)\\ 
0,& \text{if } (0< \gamma < 1)\wedge(m=2)\\ 
\gamma x^p,& \text{if } (0< \gamma < 1)\wedge(m=3)\\ 
\end{cases}\\\\

RScont(x^a(t),x^p(t),t,\gamma) = RSvel(0,x^a(t),x^p(t),t,\gamma) + \begin{cases} 
x^a,& \text{if } (0< \gamma < 1)\wedge(m=1)\\ 
x^a,& \text{if } (0< \gamma < 1)\wedge(m=2)\\ 
(1-\gamma)x^a,& \text{if } (0< \gamma < 1)\wedge(m=3)\\
0 ,& \text{otherwise}\\ \end{cases}\\\\

f_{ref} = RS(f_{rec}^a, f_{rec}^p,t,\gamma_{rep})\\
\beta_{ref} = RS(\beta_{rec}^a, \beta_{rec}^p,t,\gamma_{rep})\\
p_{ref} = RS(p_{rec}^a, p_{rec}^p,t,\gamma_{rep})\\
q_{1,ref} = RS(q_{1,rec}^a, q_{1,rec}^p,t,\gamma_{rep})\\

\dot{q}_{1,ref} = RSvel(\dot{q}_{1,rep},\dot{q}_{1,rec}^a, \dot{q}_{1,rec}^p,t,\gamma_{rep})\\

v_{ref} = RSvel(v_{rep},v_{rec}^a, v_{rec}^p,t,\gamma_{rep})\\
\alpha_{ref} = RSvel(\alpha_{rep},\alpha_{rec}^a, \alpha_{rec}^p,t,\gamma_{rep})\\
R_{ref} = 
\begin{cases} 
R^a_{rec},& \text{if } \gamma \leq 0\\
R_{rec}^p,& \text{if } \gamma \geq 1\\

R_{rec}^p,& \text{if } (0< \gamma < 1)\wedge(m=0)\\ 
R_{rep},& \text{if } (0< \gamma < 1)\wedge(m=1)\\ 
I,& \text{if } (0< \gamma < 1)\wedge(m=2)\\ 
R_{rep}(R_{rep}^TR_{rec})^\gamma,& \text{if } (0< \gamma < 1)\wedge(m=3)\text{Klopt deze interpolatie???}\\ 
\end{cases}\\\\
% definition
% - ff: f, beta
% - velocities: dq_1, v, alpha, 
% - positions: p, q_1
% - rotations: R

% RE:
% - ff, velocities: hold
% - position: integrate
% - rotations: :)

% Rs:
% - ff, positions: default
% - velocities: hold
% - rotations: :)

>>>>

\text{\textbf{Reference Spreading}}\\
\varphi  \quad \text{Time of impact}\\
\gamma  \quad \text{Normalized time since impact}\\
T  \quad \text{Duration of interim impact mode}\\
m \quad \text{Intermediate impact mode selector (0: no RS, 1: Jari, 2: Sven, 3: mixing)}\\
j \quad \text{Number of jumps that have occured}\\\\
\text{\textbf{Sub- and superscripts}}\\
(\cdot)_{dem} \quad \text{Signals from VR device during recording}\\
(\cdot)_{rec} \;\quad \text{Signals measured from robot or calculated during recording}\\
(\cdot)_{ext} \;\quad \text{Signals resulting from the splitting and extending of the recorded signal}\\
(\cdot)_{ref} \;\quad \text{Signals determined using RS scheme}\\
(\cdot)_{rep} \;\quad \text{Signals measured from robot or calculated during replay}\\
\end{array}$
\newpage
\section*{Recording}

@@

\section*{Replaying}
$\begin{array}{l}
\ddot{q}_{rep} = \min\limits_{\ddot{q}}\left \|  \begin{bmatrix}
\alpha(\ddot{q})\\ 
a(\ddot{q})
\end{bmatrix} - \Lambda^{-1}(f_{rep}+f_{ref}) \right \| + \left \|\ddot{q}_1-(\beta_{rep}+\beta_{ref}) \right \|\\\\
f_{rep} =2(\Lambda K_{rep})^{\frac{1}{2}} \begin{bmatrix}
\omega_{ref} - \omega_{rep}
\\ 
v_{ref}-v_{rep}
\end{bmatrix} + K_{rep} \begin{bmatrix}
R_{rep}(\log({R_{rep}}^TR_{ref}))^{\vee }\\ 
p_{ref}-p_{rep}
\end{bmatrix}\\\\
\beta_{rep} = 2\sqrt{k_{rep}}\left [ \dot{q}_{1,ref}-\dot{q}_{1,rep}  \right ] + k_{rep}\left [ q_{1,ref}-q_{1,rep}  \right ]
\end{array}$

\includegraphics[trim={1cm 17.8cm 5cm 6.5cm}, clip]{Graphics/qp.pdf}
\\
\section*{Reference Extending}
$\begin{array}{l}
S_{hold}(x,\varphi,t,j) 
= \begin{cases} 
x(\varphi_j),& \text{if } t< \varphi_j\\
x(\varphi_j),& \text{if } t> \varphi_{j+1} \\
x(t) ,& \text{otherwise}\\
\end{cases}\\
\\

S_{integ}(x,y,\varphi,t,j) 
= \begin{cases} 
x(\varphi_j)+y(\varphi_j)(t-\varphi_j),& \text{if } t< \varphi_j\\
x(\varphi_{j+1})+y(\varphi_{j+1})(t-\varphi_{j+1}),& \text{if } t> \varphi_{j+1}  \\
x(t) ,& \text{otherwise}\\
\end{cases}\\
\\

S_{rot}(R,\omega,\varphi,t,j) 
= \begin{cases} 
R(\varphi_j)e^{\omega(\varphi_j)(t-\varphi_j)},& \text{if } t< \varphi_j\\
R(\varphi_{j+1})e^{\omega(\varphi_{j+1})(t-\varphi_{j+1})},& \text{if } t> \varphi_{j+1}\\
R(t) ,& \text{otherwise}\\
\end{cases}\\
\\

\\

R_{ext,j}(t) = S_{rot}(R_{rec},\omega_{rec},\varphi_{rec},t,j)\\

\\
\begin{bmatrix} 
p_{ext,j}(t)  \\
 q_{1,ext,j}(t) 
\end{bmatrix} = S_{integ} \left (
\begin{bmatrix} 
p_{rec}\\
 q_{1,rec}
\end{bmatrix} 
,\begin{bmatrix} 
v_{rec}\\
 \dot{q}_{1,rec}
\end{bmatrix} 
,\varphi_{rec},t,j \right )\\
\\

\\
\begin{bmatrix} 
\omega_{rec}(t)\\
v_{ext,j}(t)\\
 \dot{q}_{1,ext,j}(t)\\
 f_{ext,j}(t)\\
 \beta_{ext,j}(t)
\end{bmatrix} = S_{hold} \left (
\begin{bmatrix} 
\omega_{rec}\\
v_{rec}\\
 \dot{q}_{1,rec}\\
 f_{rec}\\
 \beta_{rec}
\end{bmatrix}
,\varphi_{rec},t,j \right )\\
\\

@@

$\begin{array}{l}
\gamma = \frac{t-\varphi_{rep,j}}{T}\\

U_{jump}(x,x_{ext},\gamma,m,j) = \begin{cases} 
x_{ext,j},& \text{if } \gamma \geq 1\\

x_{ext,j},& \text{if } (\gamma < 1)\wedge(m=0)\\ 
x,& \text{if } (\gamma < 1)\wedge(m=1)\\ 
0,& \text{if } (\gamma < 1)\wedge(m=2)\\ 
\gamma x_{ext,j} ,& \text{if } (\gamma < 1)\wedge(m=3)\\ \end{cases}\\\\
\\
U_{cont}(x_{ext},\gamma,m,j) = \begin{cases} 
x_{ext,j},& \text{if } \gamma \geq 1\\

x_{ext,j},& \text{if } (\gamma < 1)\wedge(m=0)\\ 
x_{ext,j-1},& \text{if } (\gamma < 1)\wedge(m=1)\\ 
x_{ext,j-1},& \text{if } (\gamma < 1)\wedge(m=2)\\ 
\gamma x_{ext,j}+ (1-\gamma)x_{ext,j-1} ,& \text{if } (\gamma < 1)\wedge(m=3)\\ \end{cases}\\\\\\

U_{rot}(R_{ext},\gamma,m,j) = \begin{cases} 
R_{ext,j},& \text{if } \gamma \geq 1\\

R_{ext,j},& \text{if } (\gamma < 1)\wedge(m=0)\\ 
R_{ext,j-1},& \text{if } (\gamma < 1)\wedge(m=1)\\ 
R_{ext,j-1},& \text{if } (\gamma < 1)\wedge(m=2)\\ 
R_{ext,j-1}(R^T_{ext,j-1}R_{ext,j})^\gamma,& \text{if } (\gamma < 1)\wedge(m=3)\\ \end{cases}\\\\

\\

R_{ref} = U_{rot}(R_{ext},\gamma,m,j)\\

\\
\begin{bmatrix} 
p_{ref}  \\
 q_{1,ref} \\
 \dot{q}_{1,ref}\\
 f_{ref}\\
 \beta_{ref}
\end{bmatrix} = U_{cont} \left (
\begin{bmatrix} 
p_{ext}\\
 q_{1,ext}\\
 \dot{q}_{1,ext}\\
 f_{ext}\\
 \beta_{ext}
\end{bmatrix} 
,\gamma, m , j \right )\\
\\

\\
\begin{bmatrix} 
\omega_{ref}\\
v_{ref}\\
\end{bmatrix} = U_{jump} \left (
\begin{bmatrix} 
\omega_{ext,j}(t)\\
v_{ext,j}(t)\\
\end{bmatrix}
,\varphi_{rec},\gamma,m,j \right )\\
\\
